Inferring disease architecture and predictive ability\\with LDpred2-auto

### 2022-08-11 paper/paper-infer-supp.tex
save

\vspace*{7em}

@@

\begin{figure}[!h]
	%\centerline{\includegraphics[width=0.8\textwidth]{simu_hist_info}}
	\caption{ \label{fig:hist-info}}
\end{figure}

>>>>

\vspace*{7em}
\clearpage

@@

\begin{figure}[p]
\centerline{\includegraphics[width=\textwidth]{est_h2_one}}
\caption{ \label{}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=\textwidth]{est_p_one}}
\caption{ \label{}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=\textwidth]{est_alpha_one}}
\caption{ \label{}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=\textwidth]{est_r2_one}}
\caption{ \label{}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=\textwidth]{postp_calib}}
\caption{ \label{}}
\end{figure}

[ ADD THE SAME, BUT AVERAGING OVER 10 SIMUS -> CI OF THE MEAN ]

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{est_binary_h2_one}}
	\caption{All h2 estimates were transformed to the liability scale with K\_pop=K and K\_GWAS either K or 0.5 (when using Neff) \label{}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{est_binary_p_one}}
	\caption{ \label{}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{est_binary_alpha_one}}
	\caption{ \label{}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{est_binary_r2_one}}
	\caption{Transformed both r2 to the liability scale, where the inferred one using Neff used K\_GWAS=0.5  \label{}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{binary_postp_calib}}
	\caption{ \label{}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_runtimes}}
	\caption{ \label{}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_h2_p}}
	\caption{ \label{}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_h2_alpha}}
	\caption{ \label{}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_r2}}
	\caption{Height has estimated h2 of 0.555 and 0.626 -> probably too large, and why estimated r2 is too large as well. The other outliers is 695.4 (Lupus), with a very small number of cases -> should probably stop using 16 PCs \label{}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_compare_sets}}
	\caption{ \label{}}
\end{figure}
